\(ler\) : LVK (LIGO-Virgo-KAGRA collaboration) event (compact-binary mergers) rate calculator and simulator

### 2024-07-29 paper/arxiv/paper.tex
mac

\fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Hemantakumar Phurailatpam , Anupreeta More, Harsh Narola, Ng Chung Yin (Leo), Justin Janquart, Chris Van Den Broeck, Otto Akseli Hannukkala, Neha Singh, and David Keitel, (2024). \(ler\)
: LVK (LIGO-Virgo-KAGRA collaboration) event (compact-binary mergers)
rate calculator and
simulator. \textit{PendingJournal of Open Source Software}, Pending(Pending), Pending. \url{https://doi.org/10.xxxxxx/draft}}}}

@@

        \author[1]{Hemantakumar Phurailatpam}
          \author[2,3]{Anupreeta More}
          \author[4,5]{Harsh Narola}
          \author[1]{Ng Chung Yin (Leo)}
          \author[4,5,6,7]{Justin Janquart}
          \author[4,5]{Chris Van Den Broeck}
          \author[1]{Otto Akseli Hannukkala}
          \author[8]{Neha Singh}
          \author[8]{David Keitel}

>>>>

\fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Hemantakumar Phurailatpam , Anupreeta More, Harsh Narola, Ng Chung Yin (Leo), Justin Janquart, Chris Van Den Broeck, Otto Akseli Hannuksela, Neha Singh, and David Keitel, (2024). \(ler\)
: LVK (LIGO-Virgo-KAGRA collaboration) event (compact-binary mergers)
rate calculator and
simulator. \textit{PendingJournal of Open Source Software}, Pending(Pending), Pending. \url{https://doi.org/10.xxxxxx/draft}}}}

@@

        \author[1]{Hemantakumar Phurailatpam}
          \author[2,3]{Anupreeta More}
          \author[4,5]{Harsh Narola}
          \author[1]{Ng Chung Yin (Leo)}
          \author[4,5,6,7]{Justin Janquart}
          \author[4,5]{Chris Van Den Broeck}
          \author[1]{Otto Akseli Hannuksela}
          \author[8]{Neha Singh}
          \author[8]{David Keitel}
